\begin{center}
\begin{longtable}{r|p{17cm}}

% % % % % % % % %
% Revolut
% % % % % % % % %
\emph{Oct 2022} & \textbf{Software engineer} \\
\textsc{current} & \emph{at \textbf{Revolut}} \\
& Actively driving the launch of a new product - margin trading.
Independently working within the full development cycle from requirements gathering to design and implementation of technical solutions \\
& Main achievements:
\begin{itemize}
    \item Improved stocks trading analytic by calculating customer's trading performance not only in USD but also in customer's home currency.
    This \textbf{improved a user experience} and allowed for a better assessment of trading history
    \item Built integration with external broker which provides margin trading capability.
    Margin trading is expected go generate a \textbf{dozens of million turnover} in a first year
\end{itemize}\\
& Stack: \cvtag{Java} \cvtag{Guice} \cvtag{JOOQ} \cvtag{Postgres} \cvtag{Google Cloud} \\

\multicolumn{2}{c}{} \\


% % % % % % % % %
% OZON
% % % % % % % % %
\emph{Jul 2021} & \textbf{Software engineer} \\
\emph{Sep 2022} & \emph{at \textbf{OZON.ru}} \\
\emph{1y \& 3m} & OZON.ru is a leading e-commerce platform in CIS region with \textbf{60 million MAU}. \\
& Was developing services for the Catalog \& Search system.
Most of the time was developing new product features which directly influence user experience.\\
& Main achievements: 
\begin{itemize}
    \item Participated in the launch of a new product - OZON Express - grocery delivery in 15 minutes which was expected to have \textbf{GMV of 500 million USD} annually
    \item Replaced search by warehouses with a search by geolocations and delivery polygons which reduced the amount of data transmitted over the network \textbf{by hundred of times} and improved the search quality by decreasing the number of false positive results \textbf{by half}
    \item Participated in the development of a new type of advertising, which is added among other search results and looks extremely native. 
    The new type of advertising was expected to generate a \textbf{revenue of 3.5 billion USD} in the first year 
\end{itemize} \\
& Stack: \cvtag{Golang} \cvtag{GRPC} \cvtag{Protobuf} \cvtag{Redis} \cvtag{Postgres} \cvtag{Kafka} \cvtag{Kubernetes} \\

\multicolumn{2}{c}{} \\

% % % % % % % % %
% Deutsche bank
% % % % % % % % %
\emph{Jul 2019} & \textbf{Software engineer} \\
\emph{Jun 2021} & \emph{at \textbf{Deutsche Bank}} \\
\emph{2 years} & Was working in Rates \& Credit IT department. The team was responsible for maintaining and developing the infrastructure for interest rate derivatives trading.
Main achievements: 
\begin{itemize}
    \item Participated in replacing the legacy monolithic unmaintainable system by new microservices which increased the reliability of the entire system. 
    This has led to a \textbf{10-fold reduction} of the number of support calls made by traders
    \item Built an integration with new exchange platform - Markitwire. 
    It helped to automate some interest rate instruments trading which was manually done before and saved \textbf{dozens of minutes} of traders time daily.
\end{itemize} \\
& Stack: \cvtag{Java} \cvtag{Kotlin} \cvtag{Spring} \cvtag{Oracle database} \cvtag{JMS} \\

\multicolumn{2}{c}{} \\


% % % % % % % % %
% ISP RAS
% % % % % % % % %
\emph{Sep 2018} & \textbf{Junior software engineer} \\
\emph{Jun 2019} & \emph{at \textbf{Institute for System Programming of the RAS}} \\
\emph{10 months} & Developed test scenarios for load testing of Apache Ignite. Researched its properties of consistency, availability and partition tolerance using Jepsen framework. Published a paper based on the results of the study.\\
& Stack: \cvtag{Golang} \cvtag{Clojure} \cvtag{Jepsen.io} \cvtag{Apache Ignite}\\
\multicolumn{2}{c}{} \\

% \multicolumn{2}{c}{} \\

 
\end{longtable}
\end{center}